---
title: "Combining Vision, LLMs and Image Generation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Combining Vision, LLMs and Image Generation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(aiworkflow)
library(magick)
```

## Objective

In this vignette we will look at how we can leverage this package to do cool stuff. We are going to build a workflow that will analyze an existing picture, and then expand on that picture to make it into a more complete description, and use that description to generate a new image. The idea is to generate a new image that takes many elements from the original one - it will not be identical, but it's likely going to be able to replicate some of its looks, posture, and style - into a clean new one.

Let's go!

## First, a step-by-step approach

### Building the describer part

```{r, workflow with vision model}

describer <- ai_workflow() |>
  set_connector("ollama") |>
  set_model("minicpm-v:8b-2.6-q5_K_M") |>
  set_temperature(0.5) |>
  set_seed(123456789) |>
  add_vision_capability() |>
  set_n_predict(2000) |>
  encapsulate() 

```

```{r, sample image of Eugene}

image_path <- system.file("images", "Eugene_Delacroix.jpg", package="aiworkflow")

```

This is a picture of the famous French painter, Eugene Delacroix.

![](`r image_path`)

Let's recreate a picture based on that that portrait.

```{r, describing the image with a vision model}

description <- describer |>
  process_prompts(prompts = list(list(text="describe this image with high accuracy, in one paragraph.",
                                      image=image_path))) |>
  pull_final_text_answer()

```

### Adding details

```{r, workflow with a llm to detail the description}

detailer <- ai_workflow() |>
  set_connector("ollama") |>
  set_model("llama3.2:latest") |>
  set_temperature(0.5) |>
  set_seed(123456789) |>
  set_processing_skill("add_details") |>
  set_n_predict(2500) |>
  encapsulate() 

```


```{r, improving the image description}

description_w_details <- detailer |>
  process_text_prompts(text_prompts = description) |>
  pull_final_text_answer()

```

### Generating the new image

```{r, image gen workflow}

# we load the default workflow from the package
basic_workflow_path <- system.file("comfyui_workflows", "cfy_default_wflow_w_lora.json", package="aiworkflow")


# we define a first workflow to use
img_gen <- ai_workflow() |> 
  set_connector("comfyui") |>
  cfy_set_custom_workflow(comfyui_workflow_json_filepath = basic_workflow_path) |>
  cfy_set_seed(435435346761) |>
  cfy_set_checkpoint(checkpoint ="juggernautXL_v8Rundiffusion.safetensors" ) |> #a good model to use
  cfy_set_steps(steps = 25) |>
  cfy_set_negative_prompt(negative_prompt = "watermark, bad quality, worst quality, bad hands, blur, low resolution, low quality, malformed limbs, missing limbs") |>
  cfy_set_image_size(resolution = "768x1344") |>
  cfy_set_sampler(sampler = "dpmpp_2m_sde_gpu") |>
  cfy_set_scheduler(scheduler = "karras") |>
  encapsulate()

```

```{r, generating image}

new_image <- img_gen |>
  process_text_prompts(description_w_details) |>
  pull_final_image_answer()

```

```{r showing new image, out.width="50%",echo=FALSE}

new_image[[1]]

```


## Bringing all the pieces in one workflow

I kept the best part for last.
You can integrate all of these pieces into a single workflow.

```{r, single workflow definition}

full_workflow <- describer |>
  add_workflow_step(detailer) |>
  add_workflow_step(img_gen)

```

And you can now do the exact same thing with a single instruction:


```{r, running the single workflow}

new_image_2 <- full_workflow |>
  process_prompts(prompts = list(list(text="describe this image with high accuracy, in one paragraph.",
                                      image=image_path))) |>
  pull_final_image_answer()

```

And you get the following image - which is identical to the one we have already generated, as we had fixed the seed.

```{r showing new image 2, out.width="50%",echo=FALSE}

new_image_2[[1]]

```

Let's run the workflow again but change all the seeds across the workflow using the change_all_seeds function.

```{r, running the single workflow with a different seed}

new_image_3 <- full_workflow |> change_all_seeds(fixed_seed = 2135878667821) |>
  process_prompts(prompts = list(list(text="describe this image with high accuracy, in one paragraph.",
                                      image=image_path))) |>
  pull_final_image_answer()

```

And we get the following picture:

```{r showing new image 3, out.width="50%",echo=FALSE}

new_image_3[[1]]

```

## More Examples

Let me give you more examples of what can be done in this way. 

