---
title: "Combining Vision, LLMs and Image Generation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Combining Vision, LLMs and Image Generation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r knitr options, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(aiworkflow)
library(magick)
```

## Objective

In this vignette we will look at how we can leverage this package to do cool stuff. We are going to build a workflow that will analyze an existing picture, and then expand on that picture to make it into a more complete description, and use that description to generate a new image. The idea is to generate a new image that takes many elements from the original one - it will not be identical, but it's likely going to be able to replicate some of its looks, posture, and style - into a clean new one.

Let's go!

## First, a step-by-step approach

### Building the describer part

```{r, workflow with vision model}

describer <- ai_workflow() |>
  set_connector("ollama") |>
  set_model("minicpm-v:8b-2.6-q5_K_M") |>
  set_temperature(0) |> #set at 0 for the vignette, but we recommend to set a value between 0.1 and 0.5 usually
  set_seed(123456789) |>
  add_vision_capability() |>
  set_n_predict(2000) |>
  encapsulate() 

```

```{r, sample image of Eugene}

image_path <- system.file("images", "Eugene_Delacroix.jpg", package="aiworkflow")

```

This is a picture of the famous French painter, Eugene Delacroix.

![](`r image_path`)

Let's recreate a picture based on that that portrait.

```{r, describing the image with a vision model}

description <- describer |>
  process_prompts(prompts = list(list(
    text="describe this image by focusing on the subject, the look, the pose, and the colors. Use only a short paragraph",
    image=image_path))) |>
  pull_final_text_answer() 

```

### Adding details

```{r, workflow with a llm to detail the description}

detailer <- ai_workflow() |>
  set_connector("ollama") |>
  set_model("llama3.2:latest") |>
  set_temperature(0) |> #set at 0 for the vignette, but we recommend to set a value between 0.1 and 0.5 usually
  set_seed(123456789) |>
  set_processing_skill("add_details") |>
  set_n_predict(2500) |>
  encapsulate() 

```


```{r, improving the image description}

description_w_details <- detailer |>
  process_text_prompts(text_prompts = description) |>
  pull_final_text_answer()

```

This is the new description we get:

> `r description_w_details`

Now let's move on to generate an image.

### Generating the new image

First we need to set up our workflow for image generation using *ComfyUI* (we have a separate vignette focused on this topic if you want to know more). 

```{r, image gen workflow}

# we load the default workflow from the package
basic_workflow_path <- system.file("comfyui_workflows", "cfy_default_wflow_w_lora.json", package="aiworkflow")


# we define a first workflow to use
img_gen <- ai_workflow() |> 
  set_connector("comfyui") |>
  cfy_set_custom_workflow(comfyui_workflow_json_filepath = basic_workflow_path) |>
  cfy_set_seed(1234) |>
  cfy_set_checkpoint(checkpoint ="juggernautXL_v8Rundiffusion.safetensors" ) |> #a good model to use
  cfy_set_steps(steps = 25) |>
  cfy_set_cfg(cfg = 5) |>
  cfy_set_negative_prompt(negative_prompt = "watermark, bad quality, worst quality, bad hands, blur, low resolution, low quality, malformed limbs, missing limbs") |>
  cfy_set_image_size(resolution = "768x1344") |>
  cfy_set_sampler(sampler = "dpmpp_2m_sde_gpu") |>
  cfy_set_scheduler(scheduler = "karras") |>
  encapsulate()

```
Then we can generate the new image by using pipes and sending the description we have just created as a prompt for the image.

```{r, generating image}

new_image <- img_gen |>
  process_text_prompts(description_w_details) |>
  pull_final_image_answer() 

```
And this is the image we get out of this workflow:

```{r showing new image, out.width="50%",echo=FALSE}

new_image[[1]]

```
While we have built this step by step, this package can make things easier. Keep on reading.

## Bringing all the pieces in one workflow

I kept the best part for last.
You can integrate all of these pieces into a single workflow.

```{r, single workflow definition}

full_workflow <- describer |>
  add_workflow_step(detailer) |>
  add_workflow_step(img_gen) |>
  unload_models_automatically()

```

And you can now do the exact same thing with a single instruction:


```{r, running the single workflow}

new_image_2 <- full_workflow |>
  process_prompts(prompts = list(list(
    text="describe this image by focusing on the subject, the look, the pose, and the colors. Use only a short paragraph",
    image=image_path))) |>
  pull_final_image_answer()

```

And you get the following image - which is identical to the one we have already generated, as we had fixed the seed.

```{r showing new image 2, out.width="50%",echo=FALSE}

new_image_2[[1]]

```

Let's run the workflow again but change all the seeds across the workflow using the change_all_seeds function.

```{r, running the single workflow with a different seed}

new_image_3 <- full_workflow |> 
  change_all_seeds(fixed_seed = 14213213654) |>
  process_prompts(prompts = list(list(
    text="describe this image by focusing on the subject, the look, the pose, and the colors. Use only a short paragraph",
    image=image_path))) |>
  pull_final_image_answer()

```

And we get the following picture:

```{r showing new image 3, out.width="50%",echo=FALSE}

new_image_3[[1]]

```

## More Examples

Let me give you more examples of what can be done in this way. Let's load a color picture this time.

```{r, a new picture that we will use}

image_path <- system.file("images", "pexels-alipazani-2787341.jpg", package="aiworkflow")

```

```{r new picture displayed, out.width="50%",echo=FALSE}

magick::image_read(image_path)

```


Now let's try to create a picture that will take inspiration from this photograph.
We will reuse the full_workflow we have established before, and we can easily generate a picture in this way:

```{r, running the single workflow on another kind of picture}

new_image_4 <- full_workflow |> 
  change_all_seeds(fixed_seed = 213213654) |>
  process_prompts(prompts = list(list(
    text="describe this image by focusing on the subject, the look, the pose, and the colors. Use only a short paragraph",
    image=image_path))) |>
  pull_final_image_answer()

```
And this is the result:

```{r showing new image 4, out.width="50%",echo=FALSE}

new_image_4[[1]]

```
As you can see it took inspiration in many ways. It's not completely identical, but the hair color, the general pose, and background colors are well respected.

But we can also use a different model to completely change the style of the end picture.
Let's for example use a model that is made for anime. 


```{r, defining an anime image gen model}

# we define a workflow to generate anime pictures
anime_img_gen <- ai_workflow() |> 
  set_connector("comfyui") |>
  cfy_set_custom_workflow(comfyui_workflow_json_filepath = basic_workflow_path) |>
  cfy_set_seed(1234) |>
  cfy_set_checkpoint(checkpoint ="animaPencilXL_v100.safetensors" ) |> #anime model
  cfy_set_steps(steps = 30) |>
  cfy_set_cfg(cfg = 5) |>
  cfy_set_negative_prompt(negative_prompt = "watermark, bad quality, worst quality, bad hands, blur, low resolution, low quality, malformed limbs, missing limbs") |>
  cfy_set_image_size(resolution = "768x1344") |>
  cfy_set_sampler(sampler = "euler") |>
  cfy_set_scheduler(scheduler = "normal") |>
  encapsulate()

# now we integrate this workflow together with the describer we have set up earlier.
full_workflow_anime <- describer |> 
  add_workflow_step(anime_img_gen) |>
  unload_models_automatically() 
  
```


```{r, running the anime workflow this time on the same picture}

image_path <- system.file("images", "pexels-alipazani-2787341.jpg", package="aiworkflow")

new_image_5 <- full_workflow_anime |> 
  change_all_seeds(fixed_seed = 212343432) |>
  process_prompts(prompts = list(list(
    text="describe this image by focusing on the subject, the look, the pose, and the colors. Use only a short paragraph",
    image=image_path))) |>
  pull_final_image_answer()

```


```{r showing new image 5, out.width="50%",echo=FALSE}

new_image_5[[1]]

```

And with another seed:

```{r, running the anime workflow this time on the same picture, with another seed}

image_path <- system.file("images", "pexels-alipazani-2787341.jpg", package="aiworkflow")

new_image_6 <- full_workflow_anime |> 
  change_all_seeds(fixed_seed = 15445389837586) |>
  process_prompts(prompts = list(list(
    text="describe this image by focusing on the subject, the look, the pose, and the colors. Use only a short paragraph",
    image=image_path))) |>
  pull_final_image_answer()

```

You get yet another version:

```{r showing new image 6, out.width="50%",echo=FALSE}

new_image_6[[1]]

```

Let's run another picture on the same workflow. This time it's a full body pose.


```{r, a new picture using a different perspective}

image_path <- system.file("images", "pexels-alanakatok-31556429.jpg", package="aiworkflow")

```

```{r new picture from back displayed, out.width="50%",echo=FALSE}

magick::image_read(image_path)

```
We use the full_workflow_anime created above.

```{r, running the anime workflow this time on the new picture}

new_image_7 <- full_workflow_anime |> 
  change_all_seeds(fixed_seed = 1234) |>
  process_prompts(prompts = list(list(
    text="describe this image by focusing on the subject, the look, the pose, and the colors, and position of the camera vs the subject",
    image=image_path))) |>
  pull_final_image_answer()

```

And you get a fairly nice image in the same style as the original one.

```{r showing new image 7, out.width="50%",echo=FALSE}

new_image_7[[1]]

```

As you can see, when using a SDXL model, there is chance of bleeding - the color of the dress transfers easily to the hair of the person. 
