---
title: "Image Generation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Image Generation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(magick)
library(aiworkflow)
```

## Preliminary Note

The image generation process relies on ComfyUI, and for now it has been tailored to work well with [SDXL](https://huggingface.co/stabilityai/stable-diffusion-xl-base-1.0) models and its derivatives. Support for [FLUX](https://huggingface.co/black-forest-labs/FLUX.1-dev) and other models will come down the road as well. For now, you can still have a lot of fun with the numerous SDXL models available out there.

## Setup and First Workflow

In order to be able to generate images using this package, you need to have [ComfyUI](https://www.comfy.org/en/) installed on your machine or at least a machine on your network, and already active as an API service (which should be the default). The ComfyUI connector from this package will assume that it runs on the IP 127.0.0.1 and on the port 8188, but this can be customized accordingly just like do for the textual workflows.

*ComfyUI* operates with its own JSON-based workflows, that you can create by hand if you want and load with the corresponding JSON file. 
In this package we have prepared a few workflows that you can use without having to do anything on your own.

In our case you need to probably download a few models if you want to follow this vignette, as *ComfyUI* does not bring anything by default. 

### Creating the workflow

You can create a workflow by starting from a default template.
In this package we have already included *cfy_default_wflow_w_lora.json* which is a basic template that contains:

- a checkpoint loader
- a lora loader 
- 1 CLIP field for positive prompt
- 1 CLIP field for negative prompt
- A Ksampler node
- A final node to save the picture

Before you can use ComfyUI to generate images, you need to download some models. In our example below, we chose to go with:

- Checkpoint: JuggernautXL (you can get it on this [HuggingFace repo](https://huggingface.co/RunDiffusion/Juggernaut-XL-v8/tree/main))
- LORA: Pixel Base

You can find such models and more on https://civitai.com/ (careful, this site contains a lot of NSFW content if you enable certain filters, so be warned).

One of the most simple workflows you can create looks like this - you need a connector for *ComfyUI*, a comfyui workflow, here we use the default template from the package, and finally we add a checkpoint for image inference. Don't forget to encapsulate() the workflow after you have finished defining it.

```{r, image gen workflow, super simple}

# we load the default workflow from the package
basic_workflow_path <- system.file("comfyui_workflows", "cfy_default_wflow_w_lora.json", package="aiworkflow")

# the most basic workflow definition
img_gen_basic <- ai_workflow() |> 
  set_connector("comfyui") |>
  cfy_set_custom_workflow(comfyui_workflow_json_filepath = basic_workflow_path) |>
  cfy_set_checkpoint(checkpoint ="juggernautXL_v8Rundiffusion.safetensors" ) |>
  encapsulate()

```

Then, creating an image as as simple as feeding it a prompt:

```{r, generating image of dog}

dog_img <- img_gen_basic |>
  process_text_prompts("A friendly dog, looking at viewer, yellow background") |>
  pull_final_image_answer()

```

And we get this:

```{r showing image of dog,out.width="50%",echo=FALSE}

dog_img[[1]]

```

A slightly more elaborate workflow would touch on several parameters such as:

- number of steps for image generation: more than 30 are recommended for usual SDXL models.
- negative prompt definition, to explicitely say what you don't want to see
- image format (this needs to contain a max of 1024*1024 pixels for SDXL models, but you can change the format)
- the sampler to use
- the scheduler to use
- the seed (the same seed and exact same parameters will always give the same image)

and more... 

In our case we set the following parameters (and we fix the seed here):

```{r, image gen workflow}

# we define a first workflow to use
img_gen <- ai_workflow() |> 
  set_connector("comfyui") |>
  cfy_set_custom_workflow(comfyui_workflow_json_filepath = basic_workflow_path) |>
  cfy_set_seed(123456) |>
  cfy_set_checkpoint(checkpoint ="juggernautXL_v8Rundiffusion.safetensors" ) |> #a good model to use
  cfy_set_steps(steps = 25) |>
  cfy_set_negative_prompt(negative_prompt = "watermark, bad quality, worst quality, bad hands, blur, low resolution, low quality, malformed limbs, missing limbs") |>
  cfy_set_image_size(resolution = "768x1344") |>
  cfy_set_sampler(sampler = "dpmpp_2m_sde_gpu") |>
  cfy_set_scheduler(scheduler = "karras") |>
  encapsulate()

```
### Generating an image

Now let's try to generate an image from this workflow, by feeding a text prompt to it.
We use the pull_final_image_answer() function to collect the resulting image from the workflow.

```{r, generating image}

actor_img <- img_gen |>
  process_text_prompts("An hollywood actor, upper body, wearing black suit, gray background") |>
  pull_final_image_answer()

```

We get the resulting image:

```{r showing image,out.width="50%",echo=FALSE}

actor_img[[1]]

```


## Applying LORAs

The basic workflow we have loaded contains a LORA loader node (a single one in this case).

We can first get the list of loras available. 

### Adding the LORA to the workflow

It's simple. You can specify it with the cfy_set_lora function, and the cfy_set_lora_model_strength lets you specify the strength of the LORA model to apply. Usually you want this to be between 0.5 and 1.0, but this depends heavily on the LORA model used.

```{r, image gen workflow with lora}

img_gen_pixel <- ai_workflow() |> 
  set_connector("comfyui") |>
  cfy_set_custom_workflow(comfyui_workflow_json_filepath = basic_workflow_path) |>
  cfy_set_seed(123456) |>
  cfy_set_lora(lora_name = "pixel_base_model.safetensors") |>
  cfy_set_lora_model_strength(strength_model = 0.8) |>
  cfy_set_checkpoint(checkpoint ="juggernautXL_v8Rundiffusion.safetensors" ) |> #best one
  cfy_set_steps(steps = 25) |>
  cfy_set_negative_prompt(negative_prompt = "watermark, bad quality, worst quality, bad hands, blur, low resolution, low quality, malformed limbs, missing limbs") |>
  cfy_set_image_size(resolution = "768x1344") |>
  cfy_set_sampler("dpmpp_2m_sde_gpu") |>
  cfy_set_scheduler("karras") |>
  encapsulate()

```


### Generating Images With LORAs

Each LORA is trained for a specific set of keywords in the CLIP node to be activated. 
In our case, the *pixel-art-xl-v1.1* LORA is activate if you use the word *pixel art*.


```{r, generating image with pixel art lora}

actor_img_pixel_keyword <- img_gen_pixel |>
  process_text_prompts("An hollywood actor, upper body, wearing black suit, gray background, pixel art") |>
  pull_final_image_answer()

```

We get the resulting image, with a pixelated look now, provided by the LORA:

```{r showing image pixelated, out.width="50%",echo=FALSE}

actor_img_pixel_keyword[[1]]

```


Let's change the strength of the LORA model.

```{r, image gen workflow with lora low strength}

img_gen_pixel_low_lora <- ai_workflow() |> 
  set_connector("comfyui") |>
  cfy_set_custom_workflow(comfyui_workflow_json_filepath = basic_workflow_path) |>
  cfy_set_seed(123456) |>
  cfy_set_lora(lora_name = "pixel_base_model.safetensors") |>
  cfy_set_lora_model_strength(strength_model = 0.3) |>
  cfy_set_checkpoint(checkpoint ="juggernautXL_v8Rundiffusion.safetensors" ) |> #best one
  cfy_set_steps(steps = 25) |>
  cfy_set_negative_prompt(negative_prompt = "watermark, bad quality, worst quality, bad hands, blur, low resolution, low quality, malformed limbs, missing limbs") |>
  cfy_set_image_size(resolution = "768x1344") |>
  cfy_set_sampler("dpmpp_2m_sde_gpu") |>
  cfy_set_scheduler("karras") |>
  encapsulate()

```


```{r, generating image low intensity lora}

actor_img_pixel_keyword_low_lora_strength <- img_gen_pixel_low_lora |>
  process_text_prompts("An hollywood actor, upper body, wearing black suit, gray background, pixel art") |>
  pull_final_image_answer()

```

We get the resulting image with a pixel art LORA applied at low strength (0.2):

```{r showing image at low LORA strength,out.width="50%",echo=FALSE}

actor_img_pixel_keyword_low_lora_strength[[1]]

```

Let's check what happens when we specify it to be used at medium strength (0.6):

```{r, image gen workflow with lora medium strength}

img_gen_pixel_medium_lora <- ai_workflow() |> 
  set_connector("comfyui") |>
  cfy_set_custom_workflow(comfyui_workflow_json_filepath = basic_workflow_path) |>
  cfy_set_seed(123456) |>
  cfy_set_lora(lora_name = "pixel_base_model.safetensors") |>
  cfy_set_lora_model_strength(strength_model = 0.6) |>
  cfy_set_checkpoint(checkpoint ="juggernautXL_v8Rundiffusion.safetensors" ) |> #best one
  cfy_set_steps(steps = 25) |>
  cfy_set_negative_prompt(negative_prompt = "watermark, bad quality, worst quality, bad hands, blur, low resolution, low quality, malformed limbs, missing limbs") |>
  cfy_set_image_size(resolution = "768x1344") |>
  cfy_set_sampler("dpmpp_2m_sde_gpu") |>
  cfy_set_scheduler("karras") |>
  encapsulate()

```


```{r, generating image medium lora}

actor_img_pixel_keyword_medium_lora_strength <- img_gen_pixel_medium_lora |>
  process_text_prompts("An hollywood actor, upper body, wearing black suit, gray background, pixel art") |>
  pull_final_image_answer()


```

We get the resulting image with a pixel art LORA applied at medium strength:

```{r showing image at medium LORA strength,out.width="50%",echo=FALSE}

actor_img_pixel_keyword_medium_lora_strength[[1]]

```

You can clearly see that the higher the strength of the LORA applied, the more pixelated the final picture looks like. Since the *right amount* of pixelization is entirely subjective, it is up to you decide in this case what looks best.

## Generating Images with Prompt Guidance

We can first setup a LLM workflow that will help improve our initial input.

```{r, more details}

sdxl_prompter <- ai_workflow() |>
  set_connector(connector = "ollama") |>
  set_model(model_name = "llama3.1:8b-instruct-q5_K_M") |>
  set_processing_skill(processing_skill = "write_sdxl_prompt_v2") |>
  set_n_predict(1500) |>
  set_seed(123454565) |>
  set_temperature(0) |>
  encapsulate()


```

let's get an anime model this time around

```{r, anime model}
# we define a first workflow to use
img_gen_anime <- ai_workflow() |> 
  set_connector("comfyui") |>
  cfy_set_custom_workflow(comfyui_workflow_json_filepath = basic_workflow_path) |>
  cfy_set_seed(123456) |>
  cfy_set_checkpoint(checkpoint ="animaPencilXL_v100.safetensors" ) |> #a good model to use
  cfy_set_steps(steps = 30) |>
  cfy_set_negative_prompt(negative_prompt = "watermark, bad quality, worst quality, bad hands, blur, low resolution, low quality, malformed limbs, missing limbs") |>
  cfy_set_image_size(resolution = "768x1344") |>
  cfy_set_sampler(sampler = "dpmpp_2m_sde_gpu") |>
  cfy_set_scheduler(scheduler = "karras") |>
  encapsulate()

```

You can then make a workflow that will include image generation following the SDXL prompter.

```{r, making the workflow to enhance the prompt quality}

expanded_sdxl_prompt_wflow <- sdxl_prompter |>
  add_workflow_step(img_gen_anime)

```

We can then generate two images, as a comparison:

```{r, using simple image gen anime}

image_girl_simple_workflow <- img_gen_anime |> 
  process_text_prompts("A young woman, black hair, walking outside in the streets of Tokyo during the day, wearing jeans and a coat, looking at the viewer.") |>
  pull_final_image_answer()

```

This is the first result:

```{r girl image with simple sdxl workflow,out.width="50%",echo=FALSE}

image_girl_simple_workflow[[1]]

```

Now we can run the workflow that tries to improve the prompt:

```{r, using the workflow to create a better prompt}

image_girl_expanded_workflow_result <- expanded_sdxl_prompt_wflow |> 
  process_text_prompts("A young woman, black hair, walking outside in the streets of Tokyo during the day, wearing jeans and a coat, looking at the viewer.") 

# to get the result of the expanded SDXL prompt
improved_prompt <- image_girl_expanded_workflow_result[["res"]][[1]][[1]][["text"]]

# to get the final image
image_girl_optimized_workflow <- image_girl_expanded_workflow_result |> pull_final_image_answer()

```
You can see that the revised and expanded prompt became the following:

> `r improved_prompt`

And now you get this image based on that prompt:


```{r girl image after improved sdxl workflow,out.width="50%",echo=FALSE}

image_girl_optimized_workflow[[1]]

```

You are left to judge whether it's better or not. Sometimes you get something more interesting this way, sometimes you don't. Since it tends to add some extra details compared to your intial prompt, it may give you something you did not want in the first place, so prompt adherence may go down as a result.

