---
title: "Image Generation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Image Generation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(aiworkflow)
```


## Setup and First Workflow

In order to be able to generate images using this package, you need to have ComfyUI installed on your machine, and already active as an API service (which should be the default).

ComfyUI works with its own workflows, that you can create by hand if you want.
In this package we have prepared a few workflows that you can use.

### Creating the workflow

```{r, image gen workflow}

basic_workflow_path <- system.file("comfyui_workflows", "cfy_default_wflow_w_lora.json", package="aiworkflow")

img_gen <- ai_workflow() |> 
  set_connector("comfyui") |>
  cfy_set_custom_workflow(comfyui_workflow_json_filepath = basic_workflow_path) |>
  cfy_set_seed() |>
  cfy_set_checkpoint(checkpoint ="juggernautXL_v8Rundiffusion.safetensors" ) |> #best one
  cfy_set_steps(steps = 25) |>
  cfy_set_negative_prompt(negative_prompt = "watermark, bad quality, worst quality, bad hands, blur, low resolution, low quality, malformed limbs, missing limbs") |>
  cfy_set_image_size(resolution = "768x1344") |>
  cfy_set_sampler("dpmpp_2m_sde_gpu") |>
  cfy_set_scheduler("karras") |>
  encapsulate()

```
### Generating an image

Now let's try to generate an image from this workflow, by feeding a text prompt to it.
We use the pull_final_image_answer() function to collect the resulting image from the workflow.

```{r, generating image}

dog_img <- img_gen |>
  process_text_prompts("A dog sitting on the porch of a house on a sunny day") |>
  pull_final_image_answer()


```
## Applying LORAs

The basic workflow we have loaded contains a LORA loader node. 

We can first get the list of loras available. 

### Adding the LORA to the workflow

It's simple. You can specify it with the cfy_set_lora function.

```{r, image gen workflow with lora}

img_gen_pixel <- ai_workflow() |> 
  set_connector("comfyui") |>
  cfy_set_custom_workflow(comfyui_workflow_json_filepath = basic_workflow_path) |>
  cfy_set_seed() |>
  cfy_set_lora(lora_name = "pixel-art-xl-v1.1.safetensors") |>
  cfy_set_checkpoint(checkpoint ="juggernautXL_v8Rundiffusion.safetensors" ) |> #best one
  cfy_set_steps(steps = 25) |>
  cfy_set_negative_prompt(negative_prompt = "watermark, bad quality, worst quality, bad hands, blur, low resolution, low quality, malformed limbs, missing limbs") |>
  cfy_set_image_size(resolution = "768x1344") |>
  cfy_set_sampler("dpmpp_2m_sde_gpu") |>
  cfy_set_scheduler("karras") |>
  encapsulate()

```


### Generating Images With LORAs

Each LORA is trained for a specific set of keywords in the CLIP node to be activated. 
In our case, the *pixel-art-xl-v1.1* LORA is activate if you use the word *pixel art*.


```{r, generating image}

dog_img_pixel_keyword <- img_gen_pixel |>
  process_text_prompts("A dog sitting on the porch of a house on a sunny day, pixel art") |>
  pull_final_image_answer()


```
You can see that if we do not use the keyword, the picture comes back to a photographic one:

```{r, generating image}

dog_img_no_keyword <- img_gen_pixel |>
  process_text_prompts("A dog sitting on the porch of a house on a sunny day") |>
  pull_final_image_answer()

```

You can also specify the strength of the LORA model.

```{r, image gen workflow with lora low strength}

img_gen_pixel_low <- ai_workflow() |> 
  set_connector("comfyui") |>
  cfy_set_custom_workflow(comfyui_workflow_json_filepath = basic_workflow_path) |>
  cfy_set_seed() |>
  cfy_set_lora(lora_name = "pixel-art-xl-v1.1.safetensors") |>
  cfy_set_lora_model_strength(strength_model = 0.1) |>
  cfy_set_seed_change(seed_change = "random") |>
  cfy_set_checkpoint(checkpoint ="juggernautXL_v8Rundiffusion.safetensors" ) |> #best one
  cfy_set_steps(steps = 25) |>
  cfy_set_negative_prompt(negative_prompt = "watermark, bad quality, worst quality, bad hands, blur, low resolution, low quality, malformed limbs, missing limbs") |>
  cfy_set_image_size(resolution = "768x1344") |>
  cfy_set_sampler("dpmpp_2m_sde_gpu") |>
  cfy_set_scheduler("karras") |>
  encapsulate()

```



```{r, generating image low lora}

dog_img_pixel_keyword_low_lora <- img_gen_pixel_low |>
  process_text_prompts("A dog sitting on the porch of a house on a sunny day, pixel art") |>
  pull_final_image_answer()


```



```{r, image gen workflow with lora very low strength}

img_gen_pixel_high <- ai_workflow() |> 
  set_connector("comfyui") |>
  cfy_set_custom_workflow(comfyui_workflow_json_filepath = basic_workflow_path) |>
  cfy_set_lora(lora_name = "pixel-art-xl-v1.1.safetensors") |>
  cfy_set_lora_model_strength(strength_model = 0.7) |>
  cfy_set_checkpoint(checkpoint ="juggernautXL_v8Rundiffusion.safetensors" ) |> #best one
  cfy_set_steps(steps = 25) |>
  cfy_set_negative_prompt(negative_prompt = "watermark, bad quality, worst quality, bad hands, blur, low resolution, low quality, malformed limbs, missing limbs") |>
  cfy_set_image_size(resolution = "768x1344") |>
  cfy_set_sampler("dpmpp_2m_sde_gpu") |>
  cfy_set_scheduler("karras") |>
  encapsulate()

```

```{r, test with different strengh}

dog_img_pixel_keyword_high_lora <- img_gen_pixel |>
  process_text_prompts("A dog sitting on the porch of a house on a sunny day, (pixel: 0.8)") |>
  pull_final_image_answer()

```