---
title: "Vision Models Usage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vision Models Usage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(aiworkflow)
library(magick)
```

## Basic Example

This package supports the usage of vision models. Vision models are specific models that are trained to accept images as inputs. Since most of them also support text inputs, you need to declare that you want to use their vision capabilities. Note that the package has no knowledge of the availability of vision capabilities for each model. You need to check by yourself, as most models only accept text inputs. This being said, the following models have vision capabilities and can be used with the ollama connector, at the time of writing:

- minicpm-v
- moondream
- llava
- llava-llama3
- llava-phi3
- llama3.2-vision

Once you have selected a model that is suitable for vision processing, you need to add the add_vision_capability() as part of your workflow definition for the image input to be processed.

Here is a short example:

```{r, workflow with vision model}

describer <- ai_workflow() |>
  set_connector("ollama") |>
  set_model("minicpm-v:8b-2.6-q5_K_M") |>
  set_temperature(0.5) |>
  add_vision_capability() |>
  set_n_predict(2000) |>
  encapsulate() 

```

The below picture is from the Library of Congress from the civil war era (public domain, see <https://www.loc.gov/resource/ppmsca.67667/>)

```{r, sample image}

image_path <- system.file("images", "congress_library_civil_war.jpg", package="aiworkflow")

```

This is what the picture included in our package looks like:

![](`r image_path`)

Now we use the vision model minicpm-v to get a description of this image. Note that this time, we provide a prompt with two inputs:

- a text input which is our question related to the image.
- an image input which is the path to the image we feed to the model. 


```{r, describing the image with a vision model}

description <- describer |>
  process_prompts(prompts = list(list(text="describe this image with high accuracy",
                                      image=image_path))) |>
  pull_final_text_answer()

```

You get the following description:

> `r gsub(description,pattern='\n',replacement=' ')`

## Use Cases Beyond Descriptions

### Counting entities

You can use image models to count the number of people in a picture:

```{r, counting people with vision model}

people_count <- describer |>
  process_prompts(prompts = list(list(text="count how many people are in this picture. Answer very concisely.",
                                      image=image_path))) |>
  pull_final_text_answer()

```

You get the following answer:

> `r gsub(people_count, pattern='\n',replacement=' ')`

### Probing

You can ask questions such as what kind of camera was used to produce this picture:

```{r, camera check}

camera_check <- describer |>
  process_prompts(prompts = list(list(text="what kind of camera was used to produce this picture? Answer in one paragraph only.",
                                      image=image_path))) |>
  pull_final_text_answer()

```

And you get:

> `r gsub(camera_check, pattern='\n',replacement=' ')`

### Colors

You can ask to extract the main color(s) from a picture.

```{r, colors}

main_colors <- describer |>
  process_prompts(prompts = list(list(text="Give the hexadecimal values of the main colors from this picture. Answer concisely.",
                                      image=image_path))) |>
  pull_final_text_answer()

```

And you get:

> `r gsub(main_colors, pattern='\n',replacement=' ')`

### Emotions

You can ask to confirm the emotion coming from an image.

```{r, emotions}

emotions <- describer |>
  process_prompts(prompts = list(list(
    text="Describe the emotions coming from the image, and if it is positive or negative. Answer concisely.",
    image=image_path))) |>
  pull_final_text_answer()

```

And you get:

> `r gsub(emotions, pattern='\n',replacement=' ')`

Here's another example so you can get an idea of how it changes. This time we will use [this pic](https://www.loc.gov/resource/music.musgottlieb-03141/?r=-0.572,-0.087,2.145,1.455,0) of [Dizzy Gillespie](https://en.wikipedia.org/wiki/Dizzy_Gillespie):

```{r, dizzy}

dizzy <- system.file("images", "dizzy_gillespie.jpg", package="aiworkflow")

```

![](`r dizzy`)

```{r, emotions_dizzy}

emotions_dizzy <- describer |>
  process_prompts(prompts = list(list(
    text="Describe the emotions coming from the image, and if it is positive or negative. Answer concisely.",
    image=dizzy))) |>
  pull_final_text_answer()

```

And you get:

> `r gsub(emotions_dizzy, pattern='\n',replacement=' ')`

### Reading handwriting

Let's see what vision models can do with handwritten letters. 
We will be using [a letter from WW1 era](https://en.wikipedia.org/wiki/File:Hand_written_letter_of_recognition_for_world_war_1_pow_from_king_george_v_1918_sent_to_lance_corporal_james_cordingley.jpg) as an example.

```{r, letter from ww1}

letter <- system.file("images", "historical_letter.jpg", package="aiworkflow")

```

<img src="`r letter`" alt="letter" width="100%"/>

Since we are not asking the model to be very creative here, we want to keep the temperature as low as possible. Let's define a new workflow.

```{r, workflow to read letter}

letter_reader <- ai_workflow() |>
  set_connector("ollama") |>
  set_model("llama3.2-vision") |>
  set_temperature(0.1) |>
  add_vision_capability(max_image_dimension = 600) |>
  set_n_predict(2000) |>
  encapsulate() 

```


```{r, vision model applied on letter}

letter_text <- letter_reader |>
  process_prompts(prompts = list(list(text="This is a handwritten letter. Extract the WHOLE message with high accuracy. Keep all the parts as they are, without making them shorter. There is no need to add comments before or after the text of the letter.",
                                      image=letter))) |>
  pull_final_text_answer()

```

We get the following result:

> `r gsub(letter_text, pattern='\n',replacement=' ')`

You will notice that the transcription is not perfect. This is expected, as the vision models are trained to work on a wide range of images and not just focusing on OCR. Note that some models perform better at OCR than others (moondream, for example, performs very poorly) and you probably need to test things by yourself in order to validate what is the right model for your use case.

### Reading graphs

We can also ask vision models to describe data included in charts or graphs. Since this is rather specific use case, we modify the system prompt a little bit to make sure it will focus on understanding the data behind the charts.

```{r, workflow to read graphs}

chart_analyzer <- ai_workflow() |>
  set_connector("ollama") |>
  set_model("llama3.2-vision") |>
  set_temperature(0) |>
  set_system_prompt("You are an AI model specialized in reading data from charts and graphs.") |>
  add_vision_capability() |>
  set_n_predict(2000) |>
  encapsulate() 

```
Let's provide it with a chart of the [Operating Systems share over time](https://flatworldknowledge.lardbucket.org/books/designing-business-information-systems-apps-websites-and-more/s13-02-representing-industry-informat.html), between 2009 and 2010. 

```{r, chart image}

os_chart <- system.file("images", "operating_system_share.png", package="aiworkflow")

```

<img src="`r os_chart`" alt="chart of os share" width="100%"/>


```{r, vision model applied on chart}

chart_explanation <- chart_analyzer |>
  process_prompts(prompts = list(list(text="Explain what this chart represents, and what we can conclude from it. Keep your explanation in one paragraph.",
                                      image=os_chart))) |>
  pull_final_text_answer()

```

We get the following description:

> `r gsub(chart_explanation, pattern='\n',replacement=' ')`

A pretty accurate statement in this case.

## Automatic Image Resizing

In order to speed up the inference from the model, you can specify your workflow to resize images that are bigger than a certain dimension on the fly, before they are fed to the model. You can do this by using the parameter *max_image_dimension* inside the add_vision_capability function. The number you provide will be the maximum image dimension (x or y, whichever is greater) that we will feed to the model. This functionality uses the excellent *magick* library behind the scenes.

In the example below we will resize Dizzy's picture to 400 pixels.

```{r, workflow with vision model, with resizing to 400 pixels}

describer_400 <- ai_workflow() |>
  set_connector("ollama") |>
  set_model("minicpm-v:8b-2.6-q5_K_M") |>
  set_temperature(0.1) |>
  add_vision_capability(max_image_dimension = 400) |>
  set_n_predict(2000) |>
  encapsulate() 

```


```{r, testing resizing at 400}

dizzy_400 <- describer_400 |>
  process_prompts(prompts = list(list(text="Describe what is pictured in this image, in one paragraph.",
                                      image=dizzy))) |>
  pull_final_text_answer()

```

We get the following description:

> `r gsub(dizzy_400, pattern='\n',replacement=' ')`

It still works well at 400px, as you can see. Let's try now by shrinking the picture down to 200 pixels.

```{r, workflow with vision model, with resizing set at 200}

describer_200 <- ai_workflow() |>
  set_connector("ollama") |>
  set_model("minicpm-v:8b-2.6-q5_K_M") |>
  set_temperature(0.1) |>
  add_vision_capability(max_image_dimension = 200) |>
  set_n_predict(2000) |>
  encapsulate() 

dizzy_200 <- describer_200 |>
  process_prompts(prompts = list(list(text="Describe what is pictured in this image, in one paragraph.",
                                      image=dizzy))) |>
  pull_final_text_answer()

```

We get the following description:

> `r gsub(dizzy_200, pattern='\n',replacement=' ')`

Impressive! We did not lose much information apparently. Let's go down even further to 50 pixels.

```{r, workflow with vision model, with resizing set at 50}

describer_50 <- ai_workflow() |>
  set_connector("ollama") |>
  set_model("minicpm-v:8b-2.6-q5_K_M") |>
  set_temperature(0.1) |>
  add_vision_capability(max_image_dimension = 50) |>
  set_n_predict(2000) |>
  encapsulate() 

dizzy_50 <- describer_50 |>
  process_prompts(prompts = list(list(text="Describe what is pictured in this image, in one paragraph.",
                                      image=dizzy))) |>
  pull_final_text_answer()

```
At 50 pixels, we are reaching the limit:

> `r gsub(dizzy_50, pattern='\n',replacement=' ')`

The description is now severely impaired - we went too far in reducing the image size.